%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Tam Wing Fan Innovation Wing} % Organization
    {Hong Kong SAR} % Location
    {Jun. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained BERT-based language models for text classification, enhancing contextual awareness by using domain specific pre-training.}
        \item {Architected and built a full-stack application with user management system with Next.js, MongoDB, and TailwindCSS to serve as the primary model interface.}
        \item {Deployed scalable RESTful API endpoints to deliver real-time model inferences between the backend LLM model, database, and the user-facing application.}
        \item {Research is supervised under Professor Kao, Benjamin C.M of The University of Hong Kong}
      \end{cvitems}
    }


  \cventry
    {Software Engineer} % Job title
    {PT. Moxcal Teknologi} % Organization
    {Jakarta, Indonesia} % Location
    {May 2024 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a web (HTML, Bootstrap, and JavaScript) and WhatsApp based AI chatbot solution and user interface to automate customer support:}
        \item {Built a Natural Language Processing (NLP) framework to accurately classify user intent and extract key entities (NER) from user messages.}
        \item {Enabled the chatbot to communicate through both text and natural-sounding speech through voice recognition and text-to-speech.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
