\cvsection{Projects}

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {TypeScript, Next.js, PostgreSQL, Azure} % Stack
    {Arang} % Title
    {} % Leave empty
    {Oct. 2024} % Date
    {
      \begin{cvitems} % Description(s)
        \item {Arang is a \textbf{spaced repetition} algorithm flashcards app which combines traditional digital flashcards
functionality with LLM models using \textbf{Retrieval Augmented Generation} (RAG) to intelligently generate
flashcards questions and answers based on images, text, and videos.}
        \item {\textbf{Full-stack web application} written in TypeScript, using the \textbf{Next.js framework with PostgreSQL} as
backend database. The app connects to Azure's OpenAI service as the LLM provider.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {TypeScript} % Stack
    {Timeblockr} % TItle
    {} % Leave empty
    {Jan. 2025 - Present} % Date
    {
      \begin{cvitems} % Description(s)
        \item {Smart AI assisted calendar which uses \textbf{RAG} to retrieve and read existing calendar lists e.g. Google Calendar, connects to \textbf{Google Maps and OpenWeather} to intelligently
assign time slots.}
        \item {AI recommendations and schedule adjustments based on \textbf{real time data} such as traffic data and weather
        forecasts.}
        \item {LLM (hosted in Azure) used are given a custom prompt and \textbf{fine-tuned with datasets} to improve output consistency and accuracy.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
